Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-20 paper/paper.tex
Revise the note for the map #58

\begin{figure}[ptb]
\caption{Unrecognized States in the Former Soviet Union}
\includegraphics[width=\linewidth]{map.png}
\label{map}%
{\scriptsize \textbf{Notes}: 
	The data sources are GADM (2018) for international boundaries and for Transnistria; ACASIAN (2014) for Abkhazia and South Ossetia; and Armenian Ministry of Foreign Affairs (2018) for Nagorno-Karabakh. WGS 1984 is used as the coordinate system to draw the map.
}
\end{figure}

>>>>

\begin{figure}[ptb]
\caption{Unrecognized States in the Former Soviet Union}
\includegraphics[width=\linewidth]{map.png}
\label{map}%
{\scriptsize \textbf{Notes}: 
	This map is drawn based on GADM (2018) for international boundaries and for Transnistria; ACASIAN (2014) for Abkhazia and South Ossetia; and Armenian Ministry of Foreign Affairs (2018) for Nagorno-Karabakh. WGS 1984 is used as the coordinate system.
}
\end{figure}
